More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-02-14 2016-Weak-FH-Bisim/WeakBisim.tex
corrections

So we need to prove that the following holds:\\

@@

The conjunction with the term $\Pred^2\subst{\Post^1}$ of the both sides of the implication, we get:\\  

@@

$\forall p \in [0..(n_1+n_2+2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
				{{\Post_p^b}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n'-1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)..(n_k-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\\
\Post^b_k=\bigotimes_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)
$\\

@@

We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0.. \alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..n_1+n_2+1] \land \alpha_p\neq \tau$.
%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

>>>>

So we need to prove that the following statement holds:\\

@@

The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  

@@

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
				{{\Post_p^b}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
\Post^b_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
$\\

@@

We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0.. \alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!1)] \land \alpha_p\neq \tau$.
%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
